%%%%%%%%%%%%%%%%%%%%%%%%%%%%%STORY NOTES%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   problems that's going to have to be done or started in this chapter
% 1)Why was Josh so mad at Angie? He still likes Kit and thinks Kit will say yes to Angie no matter what even after the shit she put her
%threw
% 2)Angie is going to be very hung over when she wakes up
% 3)This day is going to be only 2-3 chapters I'm making days way to long
% 4)May not have anymore with Chase for a few chapters
% 5)The crazy story line's girl's dad may end up stalking Mike. But I may just end the story line with him blacklisting his number
% 6)The Paula girl Angie mistakenly called in the last chapter is a white weasel she's very friendly. Is a waitress for Angie
% 7)Have Angie call her back because she sees her number on her phone. Paula will giggle then reply, ``Angie silly you called me'' 
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}[12px]
\usepackage{indentfirst}
\pagenumbering{gobble}
\begin {document}
\section* {Chapter 13}
\subsection* {Kit's Surprise}
    Kit opens the door at the bottom of the stairs and sees lots of people. She quickly turns around thinking she's interrupting something but is blocked my Mike who says, "Come on, Kit" Kit now nervous turns around. As she walks threw the door she hears Misty's voice say, "OK guys lets get this party started" A loud electronic beat fills the room. Kit is nervous and starts shaking. A bar tender is at the bar entertaining people. She is surprised it's not Angie since that's her favorite part of working then she sees Angie walk out in a pants suit with a ear piece in her ear talking. She smiles when she sees, Kit. She then holds a button on the the receiver on her hip. Then Kit hears, "Everyone quiet please", over the intercom. \\

    Angie walks up to Kit, pulling out a ring case. Kit is confused what's going on. She then says, "Kit. We first met back in kindergarten. A bigger girl was picking on you. I shoved her into some blocks causing her to run crying to the teacher. Then some years later you came to me crying. Your fur messed up and your dress torn. You ran into my arms and cried, 'Bill tried to rape me' I knew right then but I didn't want to admit it that I wanted to be with you forever." Kit is very nervous, she doesn't know what to think so she just stands there.\\

    Angie takes a deap breath and gets down on a knee. Kit gasps and covers her mouth. Angie looks up and says, "Christina Dawn Mathews", she pauses looking up at her, "Will you marry me?" Kit is struck and speechless. She loves Angie a lot and wants to be with her always but she can't answer. She just gets pictures of Jullian walking in with a gun pointed to her. She then sees another of her and Julliane naked in bed with each other. She then remembers Angie telling her, "She's going back out with Julianne" A tear runs down Kit's cheek mostly out of humiliation from being put in the spotlight.\\

    She then says, trying to sound mad, "I can't believe you would ask me this" Angie blinks shocked so does everyone else. Kit continues, "You cheated on me. You broke up with me just to go out with your cheating ex. Then that ex tried to kill me two times." Kit cries a little. "Now you put on this big show to make me think you've changed. Your still the same self centered bitch you where then" Angie still on her knee says, "Kit I did all this for you" Kit is getting mad and now with a wet face says, "No you did this for you. You just wanted a chance to show off your money, and the fact you own a bar. Hell  you used your own workers" Angie shrugs and says, "I'm already paying them" Kit now mad says, "Shut up, Angie! If you knew me and wanted to do this for me. You'd taken me to that fancy restraint and slid the ring on my finger, and proposed to me there. But no you had to show off. You had to do a big presentation" She's now shaking mad. She looks at Spec and says, "Come on Spec and Cindy" She takes his hand and says, "Lets go upstairs" Angie stands up baffled and says, "What are you doing?" Kit smirks saying, "You try to fuck him", pauses, "I am fucking him" She then pulls him upstairs.

    Angie looks around after she leaves and says, "I guess the party's over" Sorry guys. She feels a empty feeling and goes up stairs. She don't want to cry in front of people. The guest are speechless. \\

    As she passes Kit's room she hears the bed squeaking and hears her moaning. Angie frowns and shakes her head going into her room. Only to see Jessy laying on her bed watching a video on her phone. Angie says, "Hey Jes" Jessy rolls her eyes and says, "The party's over early" Angie shakes her head and says, "I ain't talking about it" Jessy shrugs and says, "She said no huh?" Angie frowns and says, "Better get ready Beth and Vicky are probably about ready to go" Jessy laughs and says, "Congratulations bitch. Mom and dad said I'm in your custody that I'm", in a baby voice, "a kid still" Angie frowns and says, "I take your home coming didn't go good" She shrugs and says, "For you" Angie confused and still baffled about what happened. She can also hear Kit getting louder. Jessy sees her looking toward her, and says, "Yeah told you she's a bit of a screamer" Angie replies, "I think this is the first time I actually feel bad. I just want to go in there and kick the door down and" Jessy laughs and says, "Oh so your jealous"

    Angie don't reply but when she hears Kit moan, "Oh Cindy suck my tit harder" She stands up ready to go. But Jessy says, "You know they're probably in there acting" Angie snarls and says, "How do you know that?" Jessy says, "First Spec ain't moaning. Second the bed ain't hitting the wall so that means Kit must be fucking him. But that would also mean when she talks that her words would be more spaced out. She can talk pretty easy" Angie frowns and says, "How would you know all this?" Jessy lays back and says, "Angie remember your my sister, and sometimes you would forget I was in the room when you would fuck a guy. And when I say sometimes I mean ninety percent of the time. So I could of left the room, continued to play with my dolls in your closet or watch and learn. I chose the second"

    Angie just says, "Wait you where in my closet?" Jessy shrugs and replies, "Yeah I played with my dolls in there all the time. Except for when you left then it wasn't fun anymore so I found other things to do" Angie groans and starts to say something but Kit's orgasm is picking up. She can't take it anymore and storms out of the room.

    She walks into Kit's room mad only to see Kit frowning on the bed. alone. Angie checks her closet and says, "Where they go?" Kit replies, "Out the front door. and by the way I'm mad at you" Angie nods looking around not believing she was fooled by what she now realizes was a trap. She never heard anyone else talking or moaning plus all the things Jessy said.

    Angie sighs in defeat and says, "Sorry Kit" Kit with a mad look and her arms crossed don't say anything. Angie waits a second then says, "How did you know I would follow?" Kit shrugs with her arms cross. Angie not liking this finally says, "Well can you at least answer me?" Again Kit shrugs her arms still crossed. Angie takes a final deep breath and leaves. After the door closes Kit takes her tail and curls up in a ball holding it. Something she's done since she was a pup and torn on something.

\subsection {Sleep Journal}
    Beth finishes putting her clothes up, and says, "So Vicky are you ready to get back to work tomorrow?" Vicky is doing the same and replies, "Not really can I have it off? Since your the boss" Beth frowns and says< "Just because your living with and screwing the boss don't mean you get special treatment" Vicky flops down on the bed and says, "Besides screwing her, living with her, and taking her to see my family" Beth sits down beside her. Vicky moves to her side and says, "So how did you like my family?" Beth rest against the headboard and says, "Yeah it was great. Now when are you going to meet mine?" Vicky laughs and says, "I thought cats never talked about their families" Beth groans and replies, "No I call my mom every day. She's looking forward to seeing you" Vicky groans and says, "Well it's only fair" She knows there's no way out of it. Beth is just going to keep asking.\\

    Vicky sighs in defeat saying, "When do I do it?" Beth smiles waiting on this and says, "Actually Since Jessy is spending the night at Kit and Angie's"" She giggles and says, "One of this days. We'll be saying that about our own little girl" Vicky blinks shocked at the comment and says, "O.... k.... So who's going to get pregnant, and how do you know it'll be a girl?" Beth kisses her and says, "Well first nether of us our men so we'll have to adopt. But thinking of it we could go get sperm donors and both get pregnant at the same time. Can you imagine giving birth at the same time?" Vicky frowns and says, "Um Beth your a doctor you know the odds of us giving birth at the same time are slim to none" Beth rolls her eyes and says, "Well since we'll both go when we happen to be ovulating at the same time. We'll get pregnant within days apart of each other if not the same time. So when one of us goes into labor the other should be far enough to have labor inseminated" Vicky blinks shocked and says, "You've put a lot of thought into this." She smiles and says, "Vicky I lived in this house completely alone for years. I could bring people from work home every night and probably get a STD or dream. I even kept journals of them" 
    
    Vicky sits up shaking her head saying, "Only a shrink would do that. I bet you even keep a sleep diary" Beth opens up her bedside table's drawer and pulls out a diary. On the front it says, 'Sleep journal' below is has the date started a hyphen and blank beside that.

    Beth smiles and says, "In case you didn't notice I put one on your side to. Beside your, ". She leans in and whispers, "Dildo" Vicky looks at her weird and says, "Beth, you don't have to whisper" Beth shrugs and says, "Best to get use to it. For when we have a little one around" Vicky smiles and says, "I never knew you wanted to be a mom this bad" Beth smiles and says, "I told you the other day" Vicky kisses her. As she's backing up she sees a glass hidden behind the lamp on Beth's' table. She then remembers her going over that direction when she things Kit ain't looking.

    Vicky points and says, "Why are you hiding your cup?" Beth shrugs and says, "It's just a night cap. You know to help me get to sleep" Vicky decides to not make anything of it and rolls on her back and says, "Man I'm tired" Beth smiles and says, "It's not even dark yet" Vicky sits up and says, "Why are  you having a night cap then?" Beth shrugs and says, "It's to help me relax" Vicky frowns and says, "Beth, I notice you do have a glass of whiskey, rum or something a lot" Beth gets up and says, "I'm getting a shower. Nothing like a shower to relax after a long drive" Vicky decides to not force the issue and says, "Want me to get one with you?" Beth shrugs and says, "I'm just getting in and out" Vicky frowns and decides to go to the kitchen to get a drink of water. 

    Vicky smiles and looks around and says, "Now where does she keep her glasses" The kitchen is pretty good size with a door to the back yard to the right of it a island with a prep station and a range with a hood. then against the wall is a large window with a sink in front of it with a stove beside that. The counter tops look like a dark grey marble with what slate floors. Both of which are kept at a bright shine. the area between the island and cabinets is enough for two people but in front of the island is a large space before you get to her large refrigerator with side by side doors. Beside that is a large cabinet. Out of curiosity she opens the door of the cabinet and sees it full of about twenty liquor bottles. She opens the bottom drawers up and sees more. She then goes to the cabinets and sees more. She blinks and says, "I think Beth's a alcoholic"

    She gets her water and goes back to the bedroom right when Beth is walking out she's got a towel wrapped around her and one around her head. Vicky also notices her staggering a bit. Finally VIcky takes a deep breath, and says, "Beth. Remember when you told me you started drinking a lot." Beth nods. Vicky then takes a deep breath and says, "Did you ever stop?" Beth sighs and says, "I see your not going to let this go" Vicky gives her a pity smile and says, "I found your stock pile while looking for a cup to get some water" Beth sits down and says, "I can't stop. I've gotten it under control, though. I drink small amounts" Vicky knows pushing her to hard won't do anything, but she says, "Beth I counted thirty bottles of liquor. That's not a little bit" 

    Beth is wanting to leave but says, "I've tried to quit. I know this isn't going to end good for me. I've tried the twelve steps, AA, even seeing a shrink" Vicky trying to lighten the mood says, "Beth looking in the mirror and talking to yourself ain't seeing a shrink" Beth frowns and says, "It is if that person has a PHD in psychology. But I went and saw a pro" Vicky nods and says, "Can I help you?" Beth sits down and says, "Please VIcky don't give me a ultimatum" Vicky puts her arm around her and says, "Never. I wouldn't put that kind of pressure on you" Beth smiles and says, "Thanks. But what kind of help do you think you can give me?" Vicky shrugs and says, "Maybe start AA again and this time I go with you" Beth smiles and says, "AA is for addicts and trust me you hear some sad stories" Vicky shrugs and says, "I know it's for addicts but isn't it true everyone is addicted to something?" Beth sighs and says, "Yeah. But does your addiction interfere with your every day life?" Vicky frowns and says, "No. It's just a caffeine addiction. But if I don't get my morning coffee I do get really bitchy" Beth laughs and says, "Vicky thanks for the offer. But this is why I relate with the drunks at work so good. I'm in their place. So hearing myself make excuses hurts but really. I'm cutting down. I'm down to a few glasses in the afternoon". Vicky shakes her head and says, "And a few at work" Beth replies, knowing what she's saying, "Well in my defence we do work in the afternoon" Vicky hugs her and says, "As long as you can keep cutting down, and please don't hide it from me" Beth nods and says, "OK"
\end {document}