% % % % % % % % % % % % % % % %STORY NOTES% % % % % % % % % % % % % % % % 
%   problems that's going to have to be done or started in this chapter %
% 1)May not have anymore with Chase for a few chapters                  %
% 2)The Paula girl Angie mistakenly called in about 3 chapters is a white weasel she's very friendly. Is a waitress for Angie
% 3)Have Angie call her back because she sees her number on her phone. Paula will giggle then reply, ``Angie silly you called me''
%
%
%
%
%
%
%
%
%
% % % % % % % % % % % % % % % %
\documentclass{article}[12px] %
\usepackage{indentfirst}      %
\pagenumbering{gobble}        %
\begin {document}             %
\section* {Chapter 13}        %
\subsection* {Fight continued}%
The next day Kit walks in the kitchen wearing the clothes she had on the day before. Angie is standing resting against the sink cabinet drinking a cup of coffee. She's looking at the floor thinking.\\

Kit groans and says, "Hey" Angie sighs and says, "Well what now?" Kit puzzled asks, "What do you mean? we're still friends" Angie replies, "Kit we can't go back to the way things where. I just proposed to you and you show me down. Now we have to decide what's next" Kit waits a second before answering, "We can always go back. I mean Angie I do love you" Angie looks up and says, "Kit, I don't want it to be weird now. I put on a huge show for you and you shot me down in front of everyone" Kit gets mad again and says, "Angie right there. You did it for you. Will you fucking listen to yourself?" \\

Angie walks out and says, "Well? It costed me a lot of money" Kit shakes her head and goes back to her room mad. Angie goes out to her car and leaves.\\

\section {Beth meets Spec}
Beth pulls up to a bookstore and sees Twilight books. She's hung over from the night before and goes inside. She walks over to the psychology books by habit but then wonders over to the fantasy fiction section.  After finding a book about a space princess that has to help rescue her prince. She goes up to check out.\\

She's never looks up she puts the book on the counter and opens her purse asking, "Do you take credit cards?" Angie is also not paying attention and says, "Yep" Beth then looks up and sees her.\\

In disbelief Beth blinks and says, "What the hell are you doing here for?" Angie still pissed at Kit says, "What does it look like Beth? I'm working. Kit wanted a fucking job so I got one with her. But no here I'm the one working while she's the one at home" Beth groans and says, "Call me later I feel like shit" Spec is walking around the store with a coffee cup in his hand, and sees Angie. He can't help but say, "So still upset about last night?" Angie looks up pissed and says, "What KIt saying I'm a self centered bitch? or the part where she embarrassed the hell out of me?" Spec laughs and replies, "Angie have you thought maybe she's right?" Angie shakes her head and says, "Fucking Beth shows up and everyone is a shrink"\\

Beth looks at Spec and says, "Do you have a degree in psychology?" Spec replies, "Navy engineer" Beth groans not feeling good. Spec then continues by asking, "Why are you here by the way". Beth groans and leaves.\\

\section* {Kit}
Kit is on the couch pissed when Jessy sits down. Jessy lays down resting her feet on Kit. Kit looks and says, "Do I look like a foot rest?" Jessy shrugs and says, "I know your pissed at my sister" Kit groans and moves Jessy's feet off of her saying, "Yes I'm mad at her she's very selfish" Jessy stands up saying, "Ain't you the one that always said, 'you want someone to show a big gesture'?" Kit groans and says, "When did I ever tell you that?" Jessy frowns and says, "I have to listen to Angie every night. that's one reason I'm wanting to move in with Beth and Vicky" Kit knows Jessy is trying to make her sister sound better. Kit sighs and says, "Does this have anything with you wanting me to be your sister?" Jessy looks innocent and won't look right at her. Before saying, "Um know why do you think that?" Kit smiles and replies, "Because you've always followed us around and even had a time where you dressed like me. It made Angie really jealous"\\

Jessy goes back to her and Angie's room without saying anything else. Kit lays on the couch thinking. She sighs and says, "What is now?"\\

Kit finally frustrated walks up stairs. She looks into Josh's room and sees him sitting on his bed watching TV. Kit smiles and walks in there saying, "Hey, why ain't you at work?" Josh shrugs and says, "Off today. Why are you here?" Kit smiles and says, "Same" Josh scoots over giving her room to sit down. After Kit sits down she says, "So why did we break up?" Josh shrugs and says, "We never dated. We screwed around started having fun then", he shrugs again, "We stopped. I waited for you to start talking to me again. Because I was going to ask you out. But then you started dating, Angie" Kit sighs replying, "We never started officially dating till not to long ago. Which is actually something for Angie. She's not really dated many people" He replies, "Thought her and Mike got pretty heated, and what about that psycho that tried to kill you and her?" Kit nods and says, "But that was only two people" Josh still looking at the tv says, "And how many have you dated" Kit thinks for a minute but gives up and says, "Ok But Todd did ask me out our sophomore year" She then makes a face thinking that Josh thinks is cute and says, "But he started dating Ashley right after that"\\

Josh turns to his side saying, "Kit, I just have to take this moment to say. The truth is you don't really know what it's like to date. You dated no one before Angie" Kit stops him and says, "You forgot about Gigi" Josh laughs and says, "Oh that annoying rabbit that never shut up?" Kit frowns and says, "She is a nice girl, and by the way. I still talk to her" Josh laughs and says, "Well she did have some huge tits" Kit groans and slaps him, playfully. Before getting up and going back downstairs to watch tv.
\end {document}