  % % % % % % % % % % % % % % %STORY NOTES% % % % % % % % % % % % % % % 
%   problems that's going to have to be done or started in this chapter %
%                                                                         % % % % % % % % % % % % % % % % % % % % % % % % % % 
% 1)The Paula girl Angie mistakenly called in about 3 chapters is a white weasel she's very friendly. Is a waitress for Angie% % %
% 2)Have Angie call her back because she sees her number on her phone. Paula will giggle then reply, ``Angie silly you called me''%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
%
%
%
%
%
%
%
%
  % % % % % % % % % % % % % %
\documentclass{article}[12px] %
\usepackage{indentfirst}      %
\pagenumbering{gobble}        %
\begin {document}             %
\section* {Chapter 15}        %
\subsection* {Kit's still mad}%
% % % % % % % % % % % % % % %
Kit sits in the couch waiting on Angie's answer. After sighing, Angie says, "Kit so is this a yes?" Kit shrugs and says, "I ain't answered you yet" Angie smiles and says, "Well your mom is waiting on a answer. I sort of already asked them if I could" KIt shrugs and says, "Tell them I'll see. I just don't want to spend the rest of my life with someone I'm not sure if they really love me or because I'm safe and they've always known me"\\

Angie groans and says, "Why won't you answer me?" Kit shakes her head and says, "If you start to understand come to my room. Otherwise go fuck yourself" Kit leaves mad. Angie shakes her head frustrated.\\

KIt lays down on her bed very mad. When she hears a knock. Thinking it's Jessy. Kit says, "Come on in" But sees Angie open the door and walk in.\\

Kit lets out a growl. Angie don't blink she just says, "Kit" Kit don't give her a chance to say anything she just says, "Angie no I don't want to watch you fuck yourself" Angie is mad that Kit won't let this go but says, "Kit I'm sorry. I just don't get what your mad about"\\

Kit sits up and says, "Angie you where proposing to me. Which means you where suppose to sweep me off my feet" Angie replies, "I tried" Kit says, "No Angie you tried to put on a huge show. So everyone will see how much you have. You have money your part owner of a club. So you spending lots of money on something. Is like a radio host saying your name on the air. It's a nice jester but don't put out any effort. Now if someone who's never on the air would do that it's a very nice jester" Angie replies, "I tried to make a huge gesture. To show you how much I cared for you" Kit sighs and says, "Angie all you did was embarrassed me. I hate being put in the spot light. You've known me since we where pups. So I'd think you'd known that" \\

Angie thinks back to her graduation. Kit had her head down and hurried across the stage. Then at the graduation dinner she tried to be alone. Angie finally says, "I always thought you where just being cool and showing you didn't care and had other things to do" Kit growls and says, "So you didn't even know I'm a dork?" Angie looks at her and says, "Now I'm getting mad. Kit you are no dork. Dorks stay to themselves while everyone else is having fun. They never" She frowns and says, "Your shy and have friends so ..." Kit groans and says, "Angie, you where my only friend. I got picked on a lot" Angie bows down and says, "Sorry Kit. But hey look at it now. Your flirting with a cute rabbit with some huge tits" Kit smiles and says, "I'm friends with her" Angie rolls her eyes and says, "Yeah. I have lots of friends like that" Kit frowns and says, "What does that mean?" Angie leans in and says, "Didn't you fuck her?" Kit thinks and says, "I can't remember" Angie nods and says, "See. You just fuck and leave. You don't even bother keeping track" Kit shakes her head and says, "Angie, please leave me alone" Angie nods and leaves.

\subsection{  }
Vicky Walks into  her and Beth's house holding hands with Beth. Vicky closes the door and says, "So Beth. How did you like the holler?" Beth smiles and says, "You're just now asking me? We've been home for a day now" Vicky shrugs and says, "Well after that disaster we just saw. It got me thinking about putting people on the spot" Beth kisses her and says, "No you didn't put me on the spot. This is natural progression I was going to have to meet your family at some point. And your going to have to meet mine" Vicky smiles and replies, "I can't wait" Beth replies, "You ain't worried?" Vicky shakes her head.\\
 
Beth smiles and says, "Well if you'd like I can arange it so you can meet them this weekend. They've been wanting to come home for some time" VIcky smiles and asks, "Do they know about you likeing girls?" Beth nods, "They didn't like the idea that I wasn't going to have babies. Since well thye really want grandkids. They kicked me out and everything but then my sister Candy got pregnant by a married man. They sort of forgot about mine. They started to assept it soon after and even apologized" Vicky nods and asks, "What happened to Candy and her baby?" Beth shrugs repying, "His wife found out about it when he was writing a child support check. She devorsed him. He went to Candy thinking she'd let him stay with her but she was still mad about him being maried. So he eneded up living in a cheap apartment paying child suport to her"
\end {document}