\documentclass {article}[12pt]
\pagenumbering {gobble}
\usepackage{indentfirst}
\begin {document}
\section* {Chapter 10}
\subsection* {Misty and the crew}
Angie is sitting on the couch in the basement listening to music. when she hears a knock on the door. She sees Misty and two moving vans parked on teh side of the street. Angie smiles and says, ``Misty there's going to be only like twenty people here. This is just a little private party nothing more. I looks like your doing a show for a hundred guest.'' Misty smiles and says, ``Angie come on. You know poeple always brings more than you expected. Anyway I'm paying for this so just sit back and relax.'' Angie nods and says, ``feels weird not doing anything.'' Misty hands her a mic and says, ``Here coordinate''.  Angie takes it then attaches the radio to her belt then the ear peice in her ear. Misty is walking people with sound equipemnt down to the basement.\\

	Angie walks around showing people where to put decorations and equipment. Angie walks up to misty and says, ``Why the equipemnt I already have a sound system here.'' Misty nods and says, ``It's just a amp for the sound table'' Angie nods and goes back to coordinated. Misty then looks at her phone after there done and says, ``What time do we show up tomarow.'' Angie says, ``I told him it starts at four so I'm expecting the guest at four thirty.'' Misty nods and says, ``Ok well be here at three. what time is the woman of honor showing up?'' Angie replies, ``Beth is supose to call me wehn they leave. it's a four hour drive so they should b here around four. But I told Beth if they show up before four to call. So I can give Kit a mondain task to do.'' Misty nods and waves her crew on and says, ``OK good luck.''\\
	
\subsection* {Angie gets a conscience}
	
\end {document}