\documentclass {article}[12pt]
\pagenumbering {gobble}
\usepackage{indentfirst}
\begin {document}
\section* {Chapter 10}
\subsection* {Misty and the crew}
Angie is sitting on the couch in the basement listening to music. when she hears a knock on the door. She sees Misty and two moving vans parked on teh side of the street. Angie smiles and says, ``Misty there's going to be only like twenty people here. This is just a little private party nothing more. I looks like your doing a show for a hundred guest.'' Misty smiles and says, ``Angie come on. You know poeple always brings more than you expected. Anyway I'm paying for this so just sit back and relax.'' Angie nods and says, ``feels weird not doing anything.'' Misty hands her a mic and says, ``Here coordinate''.  Angie takes it then attaches the radio to her belt then the ear peice in her ear. Misty is walking people with sound equipemnt down to the basement.\\

	Angie walks around showing people where to put decorations and equipment. Angie walks up to misty and says, ``Why the equipemnt I already have a sound system here.'' Misty nods and says, ``It's just a amp for the sound table'' Angie nods and goes back to coordinated. Misty then looks at her phone after there done and says, ``What time do we show up tomarow.'' Angie says, ``I told him it starts at four so I'm expecting the guest at four thirty.'' Misty nods and says, ``Ok well be here at three. what time is the woman of honor showing up?'' Angie replies, ``Beth is supose to call me wehn they leave. it's a four hour drive so they should b here around four. But I told Beth if they show up before four to call. So I can give Kit a mondain task to do.'' Misty nods and waves her crew on and says, ``OK good luck.''\\
	
\subsection* {Angie gets a conscience}
	Mike walks from his floor to the living room as the last of the crew are leaving. Curious to see what it looks like Mike walks down the basement.\\

	There's streamers hanging from the celling. Towards where the front of the house would be where the sitting area is is a table with a mixing board and other sterio equipment Mike blinks and says, ``Damn Angie when you go you go all out.'' Angie smiles and points to the table and says, ``I just needed the sound table nothing else.'' He looks at some large stage speakers and says, ``I hope poeple don't like hearing.'' Angie laughs and walks over to him holding her side and says, ``that's incase we get more than expected and is very loud.'' She shrugs and says, ``Misty plans for every posible situation.'' She points to a first ad kit and says, ``I have to admit I should of already had one down here.''\\
	
	Mike nods and asks, ``Are you nervous?'' Angie shrugs and says, ``I never thought I'd be asking her this. Yes when we where little I dreamed of me and her fooling around when we where alone but I never thought I'd be asking her to marry me.'' Mike sighs and says, ``Honestly at one time I would of sworn I'd be proposing to you. So this is a bit weird for me. I mean your asking my sister to marry you.'' 	\

	Angie smiles nad looks into his eyes and says, ``Do you ever miss what we had?'' Mike nods and says, ``Yes''. Then they lean in and begin kissing. Angie feels a sickness in her stomach before pulling back. Right as Mike reaching his arms around her. \\

	Angie takes a second and says, ``I don't know what happened but I started feeling like I was going to puck and I was sad at the same time.'' She stands there with a worried look for a second. Mike laughs and says, ``tha'ts called a conscience Angie. you feel bad for kissing osmoene other than Kit. But if it makes you feel better she does fuck her boss.'' Angie nods and says, ``We agreed a while back what we where alloud to fuck the opisite sex. just now I feel bad.'' Mike kisses her cheeck and says, ``If it makes you feel better you can call her and ask'' He's joking but Angie does think about it, befroe deciding against it. She shakes her head and says, ``I think I better finish up here. Kit will be here tomarow.''\\

	Mike walks turns to go back upstairs but stops and says, ``Angie what if she says no?'' Angie sighs and says, ``I'm expecting her to. Hell I've cheated on her broken up with her multible times. Almost gave her a break down from someoen trying to kill me that was intending to her. Honestly I think I'm a little crazy'' Mike laughs and  as he's walking up the stairs says, ``Angie that was determened a while back but honestly you belong as a Mathews we're all a little nuts.'' He stops for a seocnd then says, ``except Chase and Sarah something heppned with them. there normal''. Angie laughs and says, ``It was that chemical spill a few years ago they didn't get the water cleaned up all the way.'' Mike laughs and opens the door saying, ``Yeah tha'ts it. We're alla bunch of chemical mutants''
	
\subsection* {Chase's date}
	Chase pulls up to Heather's house right as the sun is going down. He's expecting to see her brother walk out again but sees her in a yellow sundress. He can't keep off the way they make her breast look bigger, he's resistin g the urge to comment about it as she walks in and asks how she looks. but instead he nods and says, ``You look amazing.''  She smiles and says, ``Thanks. I was worried that his was just anotehr coffee date and I was dressed up. Chase laughs and says, ``No I'm taking you to see a movie then if you don't mind I have reservations at le repas. Heather nods and says, ``Yeah there a great steak house just no idea why they named themself the meal in french''. \\
	
	There going down the road and Chase shrugs saying, ``I've heard the owner has a grreat since of humor may of just wanted to use it as a joke. Heather nods and says, ``Or if wanted to sound fancy and googled something he'd think no one would know.'' Chase nods and says, ``Well I though it was latin so I guess he fools some.'' Heather sighs and says, ``I guess being a middle school teacher helps.'' Chase laughs and says, ``Oh that's what you do. I've been wanting to ask but dind't want to sound rude'' She smiles and says, ``Yep I teach thirty or so seventh grade boys and girls health and science''\\

	Chase smiles and says, ``Health huh? I bet teaching them puberty is fun'' Heather groans and says, ``Yeah lots. I always get a few snickers when I say gonads'' Chase smiels and says, ``yeah I never knew what was so funny about that. But we're here''.\\
	
	After they see the movie tehy leave for the restraunt. Chase asks, ``So did you like it?'' Heather nervously smiles and says, ``I feell a sleep on your shoulder'' Chase smiels and replies, ``I thought you where just geting comfortable but yeah who'd thought a moive about about a talking moose that works in the tropics and takes a break every few mintues to do a monolog would be bad'' heather gets the sarcasm and says, ``The reivewers gave it a great rating'' Chase frowns and says, ``Honestly I think they pay people to give those rating or it's just one person acting like all of those giving the same rating because I tried rating on and never could find my post'' Heather smiles and says, ``Sorry'' Chase smiles and says, ``No I injoyed it''\\

	They pull into a small restraunt with windows everywhere and a roof that goes downin a angle. In the middle of the parking lot is a sign that says, ``Le repas''\\

	Chase finds a parking place behind a blue pickup, then gets out to open Heather's door. before holding hands and walking inside.\\

	Inside there taken right to there seat as soon as they walk in. Heatehr smeils and says, ``Last time I was here I had to wait a hour. This is nice.'' Chase looks at the dirty looks there geting from people waiting, and says, ``Yeah that's why I you reserve a table they guarantee they'll honor it to or your money back and a free desert.''\\
	
	Later that night Chase and her are standing on the pouch holding hands saying goodbye. Heather smiles and says, ``I had fun depite the movie being bad. The food was amazing.'' Chase nods and says, ``Yeah. want to do this again sometime?'' Heather smiles and says, ``Yes. this time lets go see a action movie.'' Chase smiles and says, ``Want to see the new superhero movie?'' Heather nods and says, ``The one with the heros no one ever heard and know everyone's jeniouses on? Or the other?'' Chase smiles and says, ``How about the Truth league?'' Heather smiles and says, ``Sounds great. See you next week'' Chase smiles and says, ``Yep'' and watches her go inside before haeding back to his car.
\end {document}