\documentclass{article}[12px]
\usepackage {indentfirst}
\pagenumbering{gobble}
\begin {document}
%This should end this day though
\section*{Chapter 11}
\subsection* {Angie gets drunk}
	Josh walks down the stairs to see Angie sitting drinking a glass of bourbon. He sits beside her and says, ``Hey so place looks nice'' Angie nods and says, ``Yeah'' He notices she is having a hard time keep her head still and asks, ``How many glasses have you had?'' Angie look at him and smiles. He knows she's drunk. He also sees a empty bottle and a half drank one.\\
	
	She reaches and grabs his crotch and says, ``We've never done it. Want to?'' Josh stands up and backs up, saying, ``Angie your drunk'' Angie grins and says, ``And I felt a big dick in those pants not a small one'' Josh looks at her weird trying to figure out how that fit in with what he said. Angie then grins and says, ``I got to pee want to watch? Kit told me you like it'' Josh getting mad says, ``Angie go to bed your way to drunk'' Angie grins and says, ``Want to help me?'' Josh knows she probably can't make it so he says, ``Yes I'll help you up the stairs. Nothing else'' Angie grins and says, ``My bed or yours? or lets get frisky and do it in Kit's'' Josh gets mad and says, ``Angie your proposing to Kit tomorrow and your trying to fuck me? Go to Hell''\\ 
	
	Angie takes another drink and says, ``I'm not married yet'', as  she watches him go up the stairs.  She then sighs and says, ``I need to talk to, Beth'' She picks up her phone and calls someone. \\
	
	A few seconds later she hears a soft cheerful voice say, ``Hey''. Angie laughs and says, ``Beth, you sound like Paula'' The voice replies, ``This is Paula is everything OK, Angie?'' Angie laughs, ``I need to speak to Beth'' Paula replies, ``Angie you sound pretty drunk won't you take a cold shower and go to bed?'' Angie laughs and says, ``OK, good night Beth'. She hangs up and says, ``I'll lay my head down''. She quickly passes out after that.\\
	
	\subsection* {Josh and Mike}
	Josh walks into Mikes room. Mike is laying on his bed watching YouTube videos. Josh sits down on his bed and says, ``Mike I just had a weird thing happen with Angie'' Mike don't look away from his screen and says, ``Josh, she shows everyone her tits. She's more proud of them than someone with fake boobs'' Josh shakes his head and says, ``No. She did that first day I met her. But she was pressuring me for sex.'' Mike groans and says, ``Josh seriously your acting like this is the first time you met the girl. She just got threw coming on to me'' Josh shakes his head and says, ``No that's not it. I mean she's suppose to be proposing to Kit tomorrow but won't stop hitting on people'' Mike shrugs and says, ``I know but hell. It's going to be catered. So I'm going to be at the buffet the whole time'' Josh stands up and shrugs saying, ``I guess I'm the only one that sees the train wreck about to happen''\\
	
	Mike starts watching the video again and says, ``It's way past train wreck. But Kit's a smart girl'' Just then he gets a text. He looks and sees a man with his hands on his hip. He's completely naked with a erection. Mike groans and says, ``Damn he used another phone'' Then he gets another one that says, ``You blocked my other number'' Mike replies, ``Leave me alone. I'm not interested''\\
	
	He gets in his app store and installed a white list app. He spends the next few minutes adding his contact list to it.\\  
	
	Chase walks into Mike's room. Mike groans and says, ``Does anyone give me privacy?'' Chase shrugs and says, ``Shut your door'\\
	' 
	He then goes over and sits on Mike's bed. Mike groans and says, ``Have a seat'' Chase shrugs and says, ``I already did'' Mike shakes his head and says, ``If you don't leave I'm going to take my pants off and expect you to suck my dick''. Chase don't blink and says, ``I've already seen you naked to many times.'' Mike shrugs and says, ``OK'' While unbuttoning his pants. Chase waves his hand towards him and says, ``OK stop. I'm gone''
	
	\subsection *{Chase}
	Chase walks into his room and says, ``Damn''. He turns on his TV then takes his PS4 controller and lays on his bed to play a game he has been trying to beat. As his character is running threw shooting Nazis he says, ``Heather feels different than other girls I dated'' He shrugs continuing to play the game and says, ``Oh well at least this one ain't trying to have sex on the first or second date. Her brother is annoying as hell but at least they're close''\\
	
	He gets a text then he looks and sees it's Heather. He smiles and sees it just says, ``Hey''. He replies, and they text for the next hour.\\
	After he gets a text that says, ``Well I'll talk tomorrow got to get some sleep''. He replies, ``Goodnight'' Then gets back to his game.
\end {document}