%%%%%%%%%%%%%%%%%%%%%%%%%%%%%STORY NOTES%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   problems that's going to have to be done or started in this chapter
% 1)Why was Josh so mad at Angie? He still likes Kit and thinks Kit will say yes to Angie no matter what even after the shit she put her
%threw
% 2)Angie is going to be very hung over when she wakes up
% 3)This day is going to be only 2-3 chapters I'm making days way to long
% 4)May not have anymore with Chase for a few chapters
% 5)The crazy story line's girl's dad may end up stalking Mike. But I may just end the story line with him blacklisting his number
% 6)The Paula girl Angie mistakenly called in the last chapter is a white weasel she's very friendly. Is a waitress for Angie
% 7)Have Angie call her back because she sees her number on her phone. Paula will giggle then reply, ``Angie silly you called me'' 
% Angie will then look at the bottle and a half of whiskey on her coffee table and say, ``How drunk did I get'' She then goes upstairs only 
% to see a pissed off Josh. Which she's clueless why he's mad so when he confronts her she don't know what he's talking about
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}[12px]
\usepackage{indentfirst}
\pagenumbering{gobble}
\begin {document}
\section* {Chapter 12}
\subsection* {The big day}
	Angie wakes up with her head throbbing. She then says, "Damn blacked out at work. I ain't done that in years". She then looks around realizing where she is and sees the empty whiskey bottle and half drank one.\\

	She looks at the clock above the bar and says, "Fuck it's ten o`clock" She stands up quick but ends up running to the trash can and vomiting.\\

	Chase walks down and sees her on the floor and runs over to her. Angie looks up and says, "Could you turn the lights off?" Chase looks around and says, "Angie it's day time that's the sun" She hands Chase her phone and says, "Here call God and tell him to kill the lights", before throwing up again.\\

	He  helps her up and says, "Here lets get a cold shower and I'll get you some ibuprofen and water" Angie replies, "I prefer to shower alone right now. I need to get ready for Kit" she then feels her pants and says, "And why is my pants wet?" Chase concerned says, "Angie no one is making you do this" Angie shakes her head and says, "I love Kit" then goes into her bathroom.\\

	In the kitchen Mike says, "Damn is she still drunk?" Chase gets the ibuprofen out and feels a big glass of water up and says, "No she just has a hang over from hell" Mike finishes his coffee and says, "Well what ever happens. We're going to be eating good tonight" Chase frowns and says, "Mike our sister might be getting married soon, and all you can think about is food?" Mike smiles and says, "I know Kit really good. I know what she's going to say", shrugs, "I'm getting ready for work"\\

\subsection* {Jessy throws a fit}
	Jessy sits down at the table and sees pancakes, sausage, bacon, and eggs. Her mom smiles and says, "Jessica, your dad and I aren't going to fight you. We talked last night and decided. Your graduated from high school, and really to young to get a full time job. So we're going to let you stay with Angie" Jessy rolls her eyes and says, "It wasn't up to you. I already told you I'm here just for a couple of days. In a few hours Vicky is going to come here and pick me up. If you don't like it I'll sneak out a window again." Her dad nods and says, "I nailed all your windows shut"\\
	
	Jessy gets mad, stands up and says, "The hell" Her mom says, "Jessica". Jessy interrupts, "It's Jessy what is so damn hard about that" She then nudges her way past them and goes to her room.\\
	
	She sits down on her bed then walks over to her window and sees her dad wasn't lying. She shakes her head and says, "They're going to imprison me here. She lays down on her bed and says, "I hate it here" Her self pity session is interrupted by a knock on the door.\\
	
	Jessy groans and says, "I don't care what you have to say" Her mom tries to open the door. Jessy laughs and says, "I locked it" She then hears some keys and the door unlocks. She screams, "THE FUCK, DAD!" Her dad walks in with her mom. They're not happy. Her dad says, "Jessica, until your eighteen your in our care. I know you think you can come and go as you please. But if your hurt or get in trouble it's on our head"\\
	
	Jessy rolls her eyes and says, "Fuck you" Her dad screams, "Jessica Amber, enough with your mouth. Remember what happened when you where twelve?" Jessica, smirks and says, "Your going to wash my mouth out again? well fuck you. You cock sucking mother fucking bi..." She's surprised with a slap to the face. Angry he says, " We where trying to be nice. We where going to make you stay here." Jessy is still holding her face, and says, "You hit me. I can call the police". He then takes off his belt and says, "Well if that's the case" Jessy rolls her eyes and says, "Get out of my room" \\
	
	Her dad is clearly raging mad. Her mom walks up to her dad and says, "Come on" Jessy rolls her eyes and says, "You to bitch" Her parents leave. She shakes her head pissed.\\
	
	After laying in there for a while she smells some food. So she goes down to get lunch. To see her mom and dad eating but nothing for her. So she says, "Where's mine?" Her dad shrugs and says, "In the store" Jessy is stunned and speechless and says, "What? It's your job to feed me" Her mom replies, "A minute ago you just made a big deal about being you own person and making your own rules. So we agreed. Your smart you graduated early and have been living with Angie for the past few months. So you can eat when you get there"\\
	
	Jessy's groans and says, "No it's your job to do this" Her dad looking down at his food replies, "This is what you wanted. You wanted us to let you do what you want. But now your wanting all the benefits of obeying our rules. You can't have your cake and eat it to"\\
	
	Jessy is mad and says, "You can't do this?" Her mom says, "Go on call the police. Tell them we're starving you and beating you. Then you'll get put into foster care and they'll make you listen and obey their rules" Jessy stands there stunned and says, "I just got blackmailed by my parents"\\
	
	Finishing his food her dad says, "OK. Now that your not screaming and thinking your big shit. Will finish what we where saying" Her mom looks up and says, "We're going to put you in the care of your sister, Angie. I thought having you spend time with Kit will help you but it seems it hasn't but this time we're going to talk to your sister so when you get home I'm sure things are going to change" Jessy rolls her eyes and laughs. There's then a car horn outside and Jessy says, "OK I don't think Angie will listen but OK", rolls her eyes, "But there waiting on me so I have to go" Jessy's parents make her hug them and she leaves.\\
\subsection* {Angie}
	Angie gets out of the shower, puts her clothes on and walks to her room. Chase walked in a bit before and put the water and medicine on the bathroom counter. She took them right after he closed the door.\\
	
	She's feeling mostly better. But knows Kit is on her way home and will be back in a few hours. Chase who's laying on the couch and he asks her if she's OK. Angie nods and goes back down to the basement.\\
	
	Once down there she pulls out her phone and calls, Misty. Jacklyn answers with, "Hey sweet stuff" Angie groans and says, "Jacklyn if I called you last night I'm sorry. I had way to much to drink and can't remember much after the fifth glass" Jacklyn laughs and says, "OK. Do you need anything?" Angie replies, "Yes why do you have Misty's phone? Second I need to talk to Misty" Jacklyn replies, "OH after I got back from outback I remembered I was suppose to get your ring for you and ran into her. We had a few drinks next thing I know I'm tied to the bed naked getting spanked with a paddle naked" \\
	
	Angie replies, "Yeah... Well I got the ring but thinks. Now is Misty near you?" Jacklyn continues, "I just have to get my other hand untied. That she forgot about last night" Angie confused asks, "She let you stay last night?" Jacklyn replies, "What is that rare?" Angie shrugs and says, "I don't know. I've never known her to fuck a girl. But oh well so can I talk to Misty?" Jacklyn replies, "Oh she's on her way to your place" Angie sighs and says, "OK that answers the question I had. Talk later". She hangs up fast and runs upstairs. \\

	Mike is walking down the stairs and Angie excited says, "Oh Mike", looks over to Chase, "When the guest start to arrive take them downstairs. I should be down there. When Kit shows up could you take her upstairs. Go fuck her or something. Hell Chase give her a bit time to remember and join in" Chase frowns and says, "Angie, I am not going to join in with Mike. But I can take her into her room and" Angie stops him and says, "No she needs to be upstairs. She'll hear the people coming in" \\

	Angie runs outside to see Misty show up in a van followed by four more vans. Angie runs up and says, "I'm sorry but we need to hide the vans. There's a parking lot behind the trees behind my house" Misty Yells for people to follow her while Angie runs threw her back yard opens the back gate. Then goes threw the trees to the parking lot.\\

	She walks out at the same time the vans are pulling in. After their parked She helps the crew and caters downstairs.\\

\subsection* {Kit's home}
	Angie has her ear piece in talking to Misty. When she hears, "The eagle has landed" She rolls her eyes but motions everyone to quiet down and cut the lights. \\

	Outside Beth pulls up to their house. Jessy steps out and getting her duffle bag and goes inside. Where Mike says, "Downstairs" Jessy throws her duffle back in her and Angie's room and goes down. Outside Beth is takeing a long time geting out of the car. Taking a few breaks and saying, "Oh I love you Vicky", kissing her then Vicky does the same. Vicky is loving the sick faces Kit is making but in reality there just taking as long as possible so everyone can get in place. 

	Finally after Kit gets out Beth turns over hitting the horn once making it look like a accident. When in reality it was code for Mike that Kit is going in. Beth opens the trunk and gets Kit's things out. \\

	Kit goes in where Mike smiles and says, "Hey sexy want to go upstairs?" Kit rolls her eyes and says, "Sorry Mike I'm tired." Mike smiles and says, "I'll get Chase to join. He can do you in the ass and I'll take the pussy" Chase walks down and says, "First I already told you. NOt in a million years. Second I'd be taking her pussy" The begin bickering back and forth. Kit rolls her eyes and goes to her room. Then flops down on her bed.\\

	Mike sees Spec and Cindy pull up she tells Chase, "Get Kit upstairs" Mike then quietly runs outside greating Spec and saying, "Hey man we have to get Kit upstairs could you wait till I open the curtains?" Spec shrugs and says, "I'll go get some coffee" Mike shrugs and says, "WHen you get back if the curtains are closed don't come in" Spec nods. then him and Cindy get back in his car and leaves.\\

	Chase walks into Kit's room and says, "Oh Kit could you come to my room. I need some advice from a girl. I'm Kind of going out with a girl named Heather now and want to talk about it" Kit looks at him wierd and says, "OK Mike being horny wasn't weird but when he said you'd join. That kind of got me thinking something is gong on. Now your wanting to talk about your feelings. What the hell is going on?" Chase rolls his eyes and says, "OK here Angie has someone in the bedroom and don't want you to see her. It's just a friend. But he I mean she" he shakes his head and says, "Sorry I was asked to call Brandy she. I new her when she was Frank" Kit looks weird and says, "OK... I'll go with you. Why is Angie so secretive about it?" Chase laughs and says, "Because she's dressed like a man. She's doing that gender bending thing" Kit laughs and says, "Oh", she shakes her head and says, "I believe it" She then follows Chase upstairs. On the way up. Kit says, "For a second I thought she was cheating on me again. But I guess if she still has a penis it ain't cheating" Chase laughs and says, "Your nice Kit"\\

	Mike waits a few seconds after Kit goes into Chase's room before opening the curtains. Spec is waiting out there in his car drinking coffee with Cindy.\\

	Mike ushers them downstairs after they go in. Mike then coughs and goes on down.\\

	Chase is showing Kit a picture of Heather and Kit says, "She's cute Chase" Chase nods and says, "OK Want a drink downstairs?" Kit shrugs and says, "KInd of tired" Chase shrugs and says, "OH well" Kit then smiles and says, "So where's Angie?" Chase replies, "Downstairs" Kit says, "I'm going to say hiy" Chase nods and says, "OK" Kit gets up quickly and goes down. Chase walks out and coughs
\end {document}